---
title: "project"
output:
  word_document: default
  html_document: default
  pdf_document: default
date: "2023-03-20"
---

```{r}

# Importing and parsing the dataset
library(mlbench)
library(caret)
data(BreastCancer)
df <- data.frame(BreastCancer)


#Partitioning training and test data
set.seed(123)
inTraining <- createDataPartition(y = df$Class, p = 0.7, list = FALSE)
training <- df[inTraining, ]
testing <- df[-inTraining, ]

```


```{r}

#################Decision tree#################

# Load the necessary packages and data
library(mlbench)
data(BreastCancer)
df <- data.frame(BreastCancer)

# Split the data into training and testing sets and remove the Id variable
set.seed(123)
train_index <- sample(nrow(df), 0.7 * nrow(df))
train <- df[train_index, -1]
test <- df[-train_index, -1]

# Create a decision tree model with the Class as the target variable
library(rpart)
model_dt <- rpart(Class ~., data = train, method = "class")

# Make predictions on the testing data
predictions_dt <- predict(model_dt, test)

# Evaluate the accuracy of the model
#accuracy_dt <- mean(predictions_dt == test$Class)

```

```{r}

#############Naive Bayes###################

# Install and load necessary packages
# Load necessary packages
library(e1071)

# Create a Naive Bayes model
model_nb <- naiveBayes(Class ~., data = train)

# Make predictions on the test dataset
predictions_nb <- predict(model_nb, test)

```

#################Random Forest#######################

# Install and load necessary packages
install.packages("randomForest")
library(randomForest)

# Check for missing values in test dataset
sum(is.na(test))

# If there are missing values, remove them
test <- na.omit(test)

# Or impute them using some method, such as mean imputation
test[is.na(test)] <- mean(train, na.rm = TRUE)

# Make predictions on the test dataset
predictions_dt <- predict(model_dt, test)

# Impute missing values in test dataset with mean value
test[is.na(test)] <- mean(test, na.rm = TRUE)

# Make predictions on the test dataset
predictions_dt <- predict(model_dt, test)

# Check for missing values in train dataset
sum(is.na(train))

# Remove missing values
train <- na.omit(train)

# Fit a random forest model
library(randomForest)
model_rf <- randomForest(Class ~ ., data = train)


# Create a random forest model
model_rf <- randomForest(Class ~., data = train)

# Make predictions on the testing dataset
predictions_rf <- predict(model_rf, test)

# Evaluate the accuracy of the model
#accuracy_rf <- mean(predictions_rf == test$Class)

##################NeuralNetwork########################

# Importing and parsing the dataset
library(mlbench)
library(caret)
data(BreastCancer)
df <- data.frame(BreastCancer)

# Partitioning training and test data
set.seed(123)
inTraining <- createDataPartition(y = df$Class, p = 0.7, list = FALSE)
training <- df[inTraining, ]
testing <- df[-inTraining, ]

install.packages("caret", dependencies = TRUE)
preproc <- preProcess(training[, -1], method = c("center", "scale"))
install.packages("caret", dependencies = TRUE, reinstall = TRUE)

# Preprocessing the data
preproc <- preProcess(training[, -1], method = c("center", "scale"))
training_scaled <- predict(preproc, training[, -1])

# Building the neural network model
library(nnet)
nnet_model <- nnet(Class ~ ., data = training_scaled, size = 5, linout = FALSE)


###3. Ensemble

# Load the dataset
library(mlbench)
library(caret)
data(BreastCancer)
df <- data.frame(BreastCancer)

# Set the seed for reproducibility
set.seed(123)

# Create a training and test dataset
trainIndex <- createDataPartition(iris$Species, p = 0.8, list = FALSE)
training <- iris[trainIndex,]
testing <- iris[-trainIndex,]

# Impute missing values using k-NN
preproc <- preProcess(training, method = "knnImpute")
train_imputed <- predict(preproc, training)
test_imputed <- predict(preproc, testing)

# Train a random forest model
model1 <- train(Species ~ ., data = train_imputed, method = "rf")

# Set up the models to be trained
models <- c("rf", "svmRadial", "knn", "gbm")

ctrl <- trainControl(method = "cv",
                     number = 10,
                     summaryFunction = multiClassSummary)


# Train an ensemble of classifiers
install.packages("caret")
library(caret)
##ensemble_model <- caretList(Species ~ ., data = train_imputed, trControl = ctrl, methodList = models, metric = "Accuracy")

# Load necessary packages
library(caret)

# Make predictions on the testing data
predicted <- predict(model_dt, test, type = "class")

# Create confusion matrix
confusionMatrix(predicted, test$Class)

# Calculate accuracy
accuracy <- confusionMatrix(predicted, test$Class)$overall["Accuracy"]

# Calculate F1 score
F1 <- confusionMatrix(predicted, test$Class)$byClass["F1"]


###########NB###########

# Load necessary packages
library(e1071)
library(caret)

# Create a Naive Bayes model
model_nb <- naiveBayes(Class ~., data = train)

# Make predictions on the test dataset
predictions_nb <- predict(model_nb, test)

# Calculate performance measures
cm_nb <- confusionMatrix(predictions_nb, test$Class)
print(cm_nb)



# Install and load necessary packages
install.packages("randomForest")
library(randomForest)

# Check for missing values in test dataset
sum(is.na(test))

# If there are missing values, remove them
test <- na.omit(test)

# Or impute them using some method, such as mean imputation
test[is.na(test)] <- mean(train, na.rm = TRUE)

# Make predictions on the test dataset
predictions_rf <- predict(model_rf, test)

# Impute missing values in test dataset with mean value
test[is.na(test)] <- mean(test, na.rm = TRUE)

# Make predictions on the test dataset
predictions_rf <- predict(model_rf, test)

# Check for missing values in train dataset
sum(is.na(train))

# Remove missing values
train <- na.omit(train)

# Fit a random forest model
library(randomForest)
model_rf <- randomForest(Class ~ ., data = train)

# Create a random forest model
model_rf <- randomForest(Class ~., data = train)

# Make predictions on the testing dataset
predictions_rf <- predict(model_rf, test)

# Create a confusion matrix
cm_rf <- table(predictions_rf, test$Class)

# Calculate accuracy
accuracy_rf <- sum(diag(cm_rf)) / sum(cm_rf)

# Calculate precision
precision_rf <- cm_rf[1,1] / sum(cm_rf[,1])

# Calculate recall
recall_rf <- cm_rf[1,1] / sum(cm_rf[1,])

# Calculate F1 score
f1_rf <- 2 * precision_rf * recall_rf / (precision_rf + recall_rf)

# Print the results
cat("Confusion Matrix and Statistics\n")
print(cm_rf)
cat("\nAccuracy :", round(accuracy_rf, 4))
cat("\nPrecision :", round(precision_rf, 4))
cat("\nRecall :", round(recall_rf, 4))
cat("\nF1 Score :", round(f1_rf, 4))



